\begin{center}
ACKNOWLEDGMENTS
\end{center}
My journey through my Computer Science degree both B.S and M.S has been an exciting one which has played a major role in my career and life, especially in enhancing my knowledge and experience in this field of study. Having had the opportunity to work with Dr.\ Gail-Joon Ahn for two years has been an insightful experience, and I am utmost grateful to him for having given me the opportunity to work on cutting edge research projects at the laboratory for Security Engineering for Future Computing (SEFCOM). Dr.\ Ahn has been a constant source of motivation through my graduate career at Arizona State University, and has contributed significantly towards my abilities in  reasoning, approaching and solving research problems impacting the society as a whole. I would like to extend my sincere gratitude to Dr.\ Partha Dasgupta  and Dr.\ Adam Doup\'e for serving on my committee and providing their valuable feedback on my thesis. 

My experience at the SEFCOM lab has provided me with great opportunities in my professional career, and has enabled me to connect with brilliant and innovative individuals who have always been there to provide valuable inputs during my research work. I would specially like to express my gratitude to Marthony Taguinod, who worked with me in the development of our test-bed for Cisco Inc. In addition to my committee and the SEFCOM lab members, I would also like to thank Cisco Inc.\ and more specifically Dr.\ Rodolfo Milito, for their support in the Fog Computing project and their valuable input during the development of our test-bed. Finally, and most importantly, I would like to extend my sincere love and regards to my parents for being a constant source of motivation and support throughout my academic career.