\chapter{DATA COLLECTION}
\label{data}


\begin{table}[tb]
\caption[\titlecap{Summary of dataset}]{Summary of Dataset} % title of Table
\centering % used for centering table
\begin{tabular}{|c| c| c|} % centered columns (4 columns)
\hline
\multicolumn{1}{|c|}{\textbf{Dataset Type}} & \multicolumn{1}{c}{\textbf{Dataset Source}} & \multicolumn{1}{|c|}{\textbf{Number of articles/ reports}}\\

\hline % inserts single horizontal line
Security Reports & External & 1000 \\ % inserting body of the table
\hline
Technical Blog Articles & External & 1500 \\
\hline
Malware Analysis Reports & Internal & 35000 \\[1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
\label{table:dataset} % is used to refer this table in the text
\end{table}


There are two sources of TI data: internal, e.g., malware analysis reports or network traces, or external, such as technical blogs or security reports. Examples of external sources include the Kaspersky whitepapers~\cite{kaspersky}, Symantec blog~\cite{symantecblog} etc. Recently, thousands of threats are reported every day, which has been broadly reported by the security companies in the form of APT/security reports~\cite{daly} or blog articles and aggressively collected by different organizations. For the scope of our research, we collected 1000 security reports and 1500 blog articles from different security organizations. All these reports and articles are published from year 2011 to 2017. Our scrapper collected information from more than 20 prominent security organization like Verizon, Symantec etc.

To bootstrap our research, we also collected around 35,000 malware reports from our in-house Cuckoo Malware Analysis System (CMAS)~\cite{oktavianto}. MAS provided some detailed results outlining what malware did when executed inside an isolated environment. While substantial volume of security reports, blog articles and malware reports are collected and analyzed, however it only constitutes a small part of the bigger IOC landscape. Summary of our dataset is in Table 1.  



