\documentclass[12pt,letterpaper]{report}
\usepackage[square,numbers]{natbib}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{afterpage}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsbsy}
\usepackage{dcolumn,array}
\usepackage{tocloft}

% for title case
\usepackage{titlecaps}
\Addlcwords{and, the, or, of, that, our, by, a, prevent, for}

% avoid widows
\usepackage[all]{nowidow}
\clubpenalty=10000

\usepackage{asudis}
%% These are for including code
%% and for upquotes
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{listingsutf8}
\usepackage{comment}
\usepackage{color}
%\usepackage{dirtytalk} % for quotations
\usepackage[justification=centering]{caption}
\usepackage[pageanchor=true,plainpages=false,pdfpagelabels,bookmarks,bookmarksnumbered,hidelinks]{hyperref}


% for footnotes in tables
\usepackage{tablefootnote}

% for arithmetic
\usepackage{xintexpr}

\usepackage{textcomp}     % access \textquotesingle

\definecolor{mygray}{rgb}{0.6,0.6,0.6}
\definecolor{lightgray}{rgb}{0.92,0.92,0.92}
\definecolor{darkgreen}{rgb}{0,0.7,0}
% default options for listings
\lstset{
	backgroundcolor=\color{lightgray},
	basicstyle=\footnotesize,
	breaklines=true, 
	captionpos=b,
	commentstyle=\color{darkgreen}, 
	frame=single,
	keywordstyle=\color{blue}, 
	numbers=left,
	numbersep=5pt,
	numberstyle=\tiny\color{mygray},
	rulecolor=\color{black},
	showstringspaces=false,
	upquote=true
}

	
\newcommand{\dq}[1]{``{#1}''}
%% THIS IS THE DATA FOR OUR THESIS, UPDATING HERE WILL UPDATE EVERYWHERE %%
\newcommand{\urls}{21,675,680\xspace}

\newcommand{\forms}{6,794,917\xspace}
\newcommand{\formsDelta}{31.35\%\xspace}

\newcommand{\emailforms}{1,132,157\xspace}
\newcommand{\emailformsDelta}{16.66\%\xspace}

\newcommand{\fuzzed}{934,016\xspace}
\newcommand{\fuzzedDelta}{82.50\%\xspace}

\newcommand{\recd}{52,724\xspace}
\newcommand{\recdDelta}{5.64\%\xspace}

\newcommand{\malfuzzed}{46,156\xspace}
\newcommand{\malfuzzedDelta}{87.54\%\xspace}

\newcommand{\success}{673\xspace}
\newcommand{\successDelta}{1.46\%\xspace}
\newcommand{\successWebsitesDelta}{0.029\%\xspace} % calc 296/1,019,921

\newcommand{\domains}{296\xspace}
\newcommand{\emailedDefaultmailbox}{111\xspace}
\newcommand{\responses}{15\xspace}
\newcommand{\confirmed}{10\xspace}
\newcommand{\ips}{413\xspace}

\newcommand{\ipsblacklist}{106\xspace}
\newcommand{\ipsblacklistmulti}{33\xspace}

\newcommand{\ehibcc}{329\xspace}
\newcommand{\ehixcheck}{396\xspace}
\newcommand{\ehito}{163\xspace}
\newcommand{\ehibccxcheck}{216\xspace}
\newcommand{\ehitoxcheck}{13\xspace}
\newcommand{\ehinuserxcheck}{219\xspace}
\newcommand{\ehiuniquenuserxcheck}{181\xspace}

% these refer to unique domains, not unique forms
\newcommand{\uniqueforms}{1,019,921\xspace}
\newcommand{\uniqueemailforms}{197,570\xspace}

\newcommand{\ehi}{E-\nobreak{}mail Header Injection\xspace}

\begin{document}
%-----------------------front matter
\pagenumbering{roman}
\title{iGen: Toward Automatic Generation and\\
 Analysis of Indicators of Compromise (IOCs)\\
 using Convolutional Neural Network}
\author{Anupam Panwar}
\degreeName{Master of Science}
\paperType{Thesis}
\defensemonth{April}
\defenseyear{2017}
\gradmonth{May}
\gradyear{2017}
\chair{Gail-Joon Ahn}
\memberOne{Adam Doup\'e}
\memberTwo{Ziming Zhao}
\maketitle
\doublespace
\include{abstract}
\dedicationpage{To my loving family and friends for their patience and support. I want to give special
note of appreciation to my late mother Madhu Panwar for her sacrifice and hard work which she
put in to teach me the importance of hardwork and being good human. She always wanted to see
me succeed. She sacrificed a lot of her personal interest and ambitions to provide all the necessary
resources needed for my success. Mom, this is for you! My twin brother Anurag motivated me to
do research and taught me never give up attitude. My father Dr. H R Panwar always supported
my decision. My elder brother Anshuman worked as catalyst for my success. Finally, I am forever
indebted to my family for their understanding, endless patience and encouragement when it was
most required.}
\include{ack}
\tableofcontents
% This puts the word "Page" right justified above everything else.
\addtocontents{toc}{~\hfill Page\par}
% Asking LaTeX for a new page here guarantees that the LOF is on a separate page
% after the TOC ends.
\newpage
% Making the LOT and LOF "parts" rather than chapters gets them indented at
% level -1 according to the chart: top of page 4 of the document at
% ftp://tug.ctan.org/pub/tex-archive/macros/latex/contrib/tocloft/tocloft.pdf
\addcontentsline{toc}{part}{LIST OF TABLES}
\renewcommand{\cftlabel}{Table}
\listoftables
% This gets the headers for the LOT right on the first page.  Subsequent pages
% are handled by the fancyhdr code in the asudis.sty file.
\addtocontents{lot}{Table~\hfill Page \par}
\newpage
\addcontentsline{toc}{part}{LIST OF FIGURES}
\addtocontents{lof}{Figure~\hfill Page \par}
\addtocontents{toc}{CHAPTER \par}
\renewcommand{\cftlabel}{Figure}
\listoffigures
% This gets the headers for the LOF right on the first page.  Subsequent pages
% are handled by the fancyhdr code in the asudis.sty file.
%----- XML Listing Configurations -------------
\definecolor{lightgray}{rgb}{.9,.9,.9}
\definecolor{darkgray}{rgb}{.4,.4,.4}
\definecolor{forestGreen}{RGB}{34,139,34}
\definecolor{orangeRed}{RGB}{255,69,0}
\definecolor{white}{RGB}{255,255,255}
 
\lstdefinelanguage{bpel}{
morekeywords={name,linkName,isolated,parallel,partnerLink,operation,portType,inputVariable,createInstance,
variable,element,location,importType,partnerLinkType,myRole,messageType,properties,level,outputVariable,
xmlns,version,encoding}
}
\lstdefinelanguage{xaml}{
morekeywords={TypeArguments,Name,Default,DisplayName,OperationName,ServiceContractName,Key,AddressUri,
CanCreateInstance, LogName, Message, MessageNumber, Expression,CorrelationHandle,Request}
}
 
\lstdefinelanguage{xml}{
        basicstyle=\small,
        sensitive=false,
}
 
\lstdefinestyle{workflowStyle}{
language=XML,
alsolanguage=bpel,
alsolanguage=xaml,
%Formatting
basicstyle=\scriptsize,
sensitive=true,
showstringspaces=false,
numbers=left,
numberstyle=\tiny,
tabsize=4,
numbersep=3pt,
extendedchars=true,
xleftmargin=2em,
lineskip=1pt,
breaklines,
captionpos=t,
%Coloring
backgroundcolor=\color{white},
morekeywords={BooleanExpression},
alsoletter={:,<,>,/,?},
morestring=[b]{"},
morecomment=[s]{<!--}{-->},keywordstyle=\color{forestGreen},
identifierstyle=\color{blue}\ttfamily,
stringstyle=\color{orangeRed}\ttfamily,
commentstyle=\color{forestGreen}\ttfamily
}
 
 
\lstnewenvironment{workflow-code}[2]{
\lstset{caption=#1,label=#2,style=workflowStyle}
}{}
%-----------------------body
\doublespace
\pagenumbering{arabic}
\include{chapter1}
\include{chapter2}
\include{chapter3}
\include{chapter4}
\include{chapter5}
\include{chapter6}
\include{chapter7}
\include{chapter8}
\include{chapter9}

%-----------------------back matter
{\singlespace
% Making the references a "part" rather than a chapter gets it indented at
% level -1 according to the chart: top of page 4 of the document at
% ftp://tug.ctan.org/pub/tex-archive/macros/latex/contrib/tocloft/tocloft.pdf
\addcontentsline{toc}{part}{REFERENCES}
\bibliographystyle{asudis}
%\bibliographystyle{unsrt}
\bibliography{dis}}
\nocite{*}
\renewcommand{\chaptername}{APPENDIX}
\addtocontents{toc}{APPENDIX \par}
\appendix
\include{appendix1}
\end{document}
